Testing Methodologies for Asynchronous Centralized Simulations\\

### 2020-12-05 paper/PaperDraft2.tex

To be developed

\subsection{Future Work}

\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
Available from ProQuest Dissertations \& Theses Global. (1881527059). 
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924

>>>>

\subsection{Future Work}
Future work would begin with a fully-realized implementation of the synthetic agent for, both, facilitating extended runtime data collection and testing as well as exploring the a fuller range of the game's runtime states. The testing utility would then include several pre-trained models minimally capable of navigating 2 and 3 dimensional environments while avoiding collisions with a generic interface for the tester(s) to provide functions specific to their environment for detecting states of collision as well as their reward signals unique to their environments.
\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
Available from ProQuest Dissertations \& Theses Global. (1881527059). 
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924
